---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
```

```{r}
tweets <- read.csv("data/code_clan_tweets.csv")
```

```{r}
tweets
```
1.Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.
Rows = 234
Columns = 27
Variable Names = 27

```{r}
ls(tweets)
names(tweets)
str(tweets)
levels(tweets)
class(tweets)
head(tweets, 5)
tail(tweets, 5)
```

2.Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
tweets %>%
  
  filter(is_quote == FALSE) %>%
  summarise(total = sum(favorite_count))

```

3.Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}
tweets %>%
  filter(is_quote == FALSE) %>%
  group_by(source) %>%
  summarise(mean == retweet_count) # wrong ???
```


4. Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.
```{r}
strings <- 
  
tweets %>% 
  
  mutate(text = str_remove(text, "[[:punct:]]")) %>% 
  mutate(text = encodeString(text)) %>% 
  mutate(tweet_length = nchar(text)) %>% 

```

5.Find the mean number of characters that a CodeClan tweet contains.
```{r}
tweets %>%
  summarise(avg_tweet_length = mean(display_text_width))
```

6.The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}

```

7.From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.

```{r}

```

8.Some tweets have more than one hashtag, denoted by the c( symbols at the start of the string. Use the str_sub() and str_detect() functions and your codeclan_hashtags tibble from above to find all the cases in which the hashtag string begins with charactersc(
```{r}
hashtags_multiple <- codeclan_hashtags %>% 
  mutate(first_letters = str_sub ????
```

