---
title: "R Notebook"
output: html_notebook
---

---
title: "R Notebook"
output: html_notebook
---


 - 5th of January 2021

Calum Sey - CodeClan Homework


```{r}
library(tidyverse)
library(here)
```

Question 1
Load the data into a dataframe project

```{r}
proj_management <- read_csv(here("data/project_management.csv"))
```


Question 2
Plot the data, taking estimated_length as the independent variable and actual_length as the dependent variable.

```{r}
data_plot <- proj_management %>% 
  ggplot() + 
  aes(x = estimated_length, y = actual_length)+
  geom_point() +
  geom_abline(
    intercept = model$coefficients[1],
    slope = model$coefficients[2],
    col = "red")

data_plot
```


Question 3
Calculate the correlation coefficient of estimated_length and actual_length and interpret the value you obtain.


```{r}
proj_management %>% 
  summarise(cor = cor(estimated_length, actual_length))
```

Having a correlation coefficient of 0.8046 it can be said that there is a stong + correlation


Question 4
Interpret the regression coefficient of estimated_length (i.e. slope, gradient) you obtain from the model. How do you interpret the r2 value reported by the model?

```{r}
model <- lm(formula = actual_length ~ estimated_length, data = project)
model
```


Question 5
Interpret the regression coefficient of estimated_length (i.e. slope, gradient) you obtain from the model. How do you interpret the r2 value reported by the model?

```{r}
library(modelr)
library(ggfortify)
```

```{r}
autoplot(model)
```

