---
title: "R Notebook"
output: html_notebook
---

Logistic regression homework

Calum Sey - CodeClan

Question 1
You have been provided some customer data from a shopping centre. Do some exploratory analysis on the data. Comment on findings.

```{r}
library(tidyverse)
library(here)
library(janitor)
library(factoextra)
library(broom)
```

```{r}
customers <- read_csv(here("data/mall_customers.csv")) %>% 
  clean_names()
```

```{r}
head(customers)
```

```{r}
summary(customers)
```

```{r}
customers %>% 
  ggplot()+ 
  aes(x = age,
      y = spending_score_1_100,
      colour = gender) + 
  geom_point()
```


```{r}
customers %>% 
  ggplot()+ 
  aes(x = annual_income_k,
      y = spending_score_1_100,
      colour = gender) + 
  geom_point()
```

Question 2
We are interested in creating a marketing campaign to target customers based on their spending score and annual income. Perform a k-means clustering to find if there are meaningful clusters in the data to target the customers.
```{r}
scaled <- customers %>% 
  select(annual_income_k,
         spending_score_1_100) %>% 
  mutate_all(scale)
```


```{r}
fviz_nbclust(scaled,
             kmeans,
             method = "wss",
             nstart = 50)
```

```{r}
fviz_nbclust(scaled,
             kmeans,
             method = "gap_stat")
```


```{r}
fviz_nbclust(scaled,
             kmeans,
             method = "silhouette",
             nstart = 50)
```

Question 3
Perform k-means clustering and chose a value of k.
```{r}
customer_clusters <- kmeans(scaled, centers = 6, nstart = 50)
customer_clusters
```

```{r}
glance(customer_clusters)
```

```{r}
customer_clusters <- augment(customer_clusters, customers)
```

Question 4
Visualise the clustering for your chosen value of k.
```{r}
library(animation)

scaled %>% 
  kmeans.ani(centers = 6) 
```


```{r}
customer_clusters %>% 
  ggplot() + 
  aes(x = annual_income_k,
      y = spending_score_1_100,
      colour = .cluster) + 
  geom_point()
```

Question 5
Do you think the clustering seems a good fit for this data?