---
title: "R Notebook"
output: html_notebook
---

Text Mining Homework 

Calum Sey - CodeClan

```{r}
library(tidyverse)
library(here)
library(janeaustenr)
library(tidytext)
```

Using the dataset austen_books() from the package janeaustenr:

1. Find the most common words in both Pride & Prejudice and Sense & Sensibility.
2. Find the most common words in both Pride & Prejudice and Sense & Sensibility, not including stop words.
3. Find the most common sentiment words in both Pride & Prejudice and Sense & Sensibility.

```{r}
head(austen_books)
```

Question 1
Find the most common words in both Pride & Prejudice and Sense & Sensibility.
```{r}
common_words <- austen_books() %>% 
  filter(book == "Sense & Sensibility" | book == "Pride & Prejudice") %>% 
  unnest_tokens(word, text) %>% 
  count(word, sort = TRUE)
common_words
```


Question 2
Find the most common words in both Pride & Prejudice and Sense & Sensibility, not including stop words.
```{r}
stop_words <- common_words %>% 
  anti_join(stop_words)
stop_words
```


Question 3
Find the most common sentiment words in both Pride & Prejudice and Sense & Sensibility.
```{r}
common_sentiment <- stop_words %>% 
  inner_join(get_sentiments("bing"))
common_sentiment
```


