---
title: "R Notebook"
output: html_notebook
---

Wed 25th of Nov 2020 - Homework - CIs

Calum Sey - CodeClan

```{r}
library(tidyverse)
library(janitor)
library(here)
```
```{r}
sample <- read_csv(here("data/ames.csv")) %>% 
  clean_names()
```

```{r}
head(sample)
```
Now we’ll go back to CI creation in the normal fashion. We’ll take the ames data from the CIs lab earlier today and regard it now as a sample, we won’t be drawing any smaller samples from within it. This is the usual situation in an analysis: you use all the data available to you!

1. Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?

```{r}
sample %>% 
  ggplot() +
  aes(x = lot_area) +
  geom_histogram(fill = "red", bins = 100)
```

There is extream values within the data set. These could be errors (unlikely, as land on this scale can be sold) or just uniqe land sales.

This will affect the results for finding the mean and ploting the sample distribution.


2. Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

```{r}
library(infer)
```

```{r}
mean_sample <- sample  %>%
  summarise(
    mean_lot_area = mean(lot_area)
  )
mean_sample
```
```{r}
bootstrap_sample <- sample %>%
  summarise(bstrap = sd(lot_area))
bootstrap_sample
```

```{r}
bootstrap_sample %>%
  ggplot(aes(x = bstrap)) +
  geom_histogram(col = "white", fill = "steel blue", alpha = 0.7)
```

--------------
here is my confusion. I understnad what Standard Deviationa and Bootstart is / means with reagrds to the data set. I think my confusion here is what are the requirements for Bootstart (do the values that are used always need to be the MEAN value). Also, without taking a sample, we only end up with one value. Which then leads to a pointles plot. I tried working the code for this, but couldn't wrap my head around it. I bet it's really simple.

The rest of the tasks don't seem like they'll give me any bother. But without the Bootstrap they will probably be invalid. I'll still write out what I would have done tho.
--------------


You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?


```{r}
ci_99_area <- bootstrap_sample %>% 
  summarise(
    mean = mean(lot_area),
    lower= quantile(mean_lot_area, probs = 0.005),
    upper = quantile(mean_lot_area, probs = 0.995)
  )
ci_99_area
```

```{r}
ci_95_area <- bootstrap_sample %>% 
  summarise(
    mean = mean(lot_area),
    lower= quantile(mean_lot_area, probs = 0.025),
    upper = quantile(mean_lot_area, probs = 0.975)
  )
ci_95_area
```


confidence interval

```{r}
infer_ci_95 <- infer_resample %>%
  get_confidence_interval(level = 0.95, type = "percentile")

infer_ci_95
```

