---
title: "R Notebook"
output: html_notebook
---

Manual model development - 7th of January 2021

Calum Sey - CodeClan

You are given a set of data on housing sale prices for the last few years in King County (near Seattle) between May 2014 and May 2015. Have a look at the variable definitions on the Kaggle page

```{r}
library(tidyverse)
library(broom)
library(ggfortify)
library(GGally)
library(here)
```

```{r}
kc_data <- read_csv(here("data/kc_house_data.csv"))
```


```{r}
head(kc_data)
```

id - Unique ID for each home sold
date - Date of the home sale
price - Price of each home sold
bedrooms - Number of bedrooms
bathrooms - Number of bathrooms, where .5 accounts for a room with a toilet but no shower
sqft_living - Square footage of the apartments interior living space
sqft_lot - Square footage of the land space
floors - Number of floors
waterfront - A dummy variable for whether the apartment was overlooking the waterfront or not
view - An index from 0 to 4 of how good the view of the property was
condition - An index from 1 to 5 on the condition of the apartment,
grade - An index from 1 to 13, where 1-3 falls short of building construction and design, 7 has an average level of construction and design, and 11-13 have a high quality level of construction and design.
sqft_above - The square footage of the interior housing space that is above ground level
sqft_basement - The square footage of the interior housing space that is below ground level
yr_built - The year the house was initially built
yr_renovated - The year of the house’s last renovation
zipcode - What zipcode area the house is in
lat - Lattitude
long - Longitude
sqft_living15 - The square footage of interior housing living space for the nearest 15 neighbors
sqft_lot15 - The square footage of the land lots of the nearest 15 neighbors


Task 1 - Tidy up the Data

You might like to think about removing some or all of date, id, sqft_living15, sqft_lot15 and zipcode (lat and long provide a better measure of location in any event).

Have a think about how to treat waterfront. Should we convert its type?

We converted yr_renovated into a renovated logical variable, indicating whether the property had ever been renovated. You may wish to do the same.

Have a think about how to treat condition and grade? Are they interval or categorical ordinal data types?

```{r}
kc_data <- kc_data %>% 
  select(-c(id, date, sqft_living15, sqft_lot15, zipcode)) %>% 
  mutate(waterfront = as.logical(waterfront)) %>% 
  mutate(renovated = as.logical(yr_renovated)) %>% 
  select(-yr_renovated) %>% 
  mutate(grade = factor(grade, levels = c(seq(1,15,1))))
```

Task 2

Check for aliased variables using the alias() function (this takes in a formula object and a data set). [Hint - formula price ~ . says ‘price varying with all predictors’, this is a suitable input to alias()]. Remove variables that lead to an alias. Check the ‘Elements of multiple regression’ lesson for a dropdown containing further information on finding aliased variables in a dataset.

```{r}
alias(lm(formula = price ~ ., data = kc_data))
```

```{r}
ggpairs(kc_data)
```


```{r}
mod1a <- lm(price ~ bedrooms, data = kc_data)
```

```{r}
autoplot(mod1a)
summary(mod1a)
```

```{r}
mod1b <- lm(price ~ grade, data = kc_data)
```

```{r}
autoplot(mod1b)
summary(mod1b)
```

```{r}
mod2a <- lm(price ~ bedrooms + sqft_living, data = kc_data)
```

```{r}
autoplot(mod2a)
summary(mod2a)
```


```{r}
mod2b <- lm(price ~ bedrooms + bathrooms, data = kc_data)
```

```{r}
autoplot(mod2b)
summary(mod2b)
```

```{r}
anova(mod1a, mod2a)
```

