---
title: "R Notebook"
output: html_notebook
---

Monday 23rd Nov 2020 - Probability homework

Calum Sey - CodeClan


 MVP - The Titanic
 
 A data set detailing the survival or death of passengers and crew members on the RMS Titanic is given in the data folder. Some time after the disaster a journalist wrote that crew members were more likely to have survived the sinking than passengers. This was disputed by a descendant of one of the surviving crew members, who suggested that the opposite was true, i.e. passengers were more likely to have survived than crew.

You’re going to calculate the conditional probabilities prob( survived ∣ crew ) and prob( survived ∣ passenger ) to settle this dispute.

Have a look at the distinct values of the class variable, this will tell you whether each individual was a passenger (1st, 2nd or 3rd class) or a member of the crew (treat restaurant staff as crew)

Loading packages

You may want to use prob and gtools later in the homework, and the tidyverse for this section, but if you load prob after tidyverse, dplyr::filter() will be masked. So load your packages in this order:

```{r}
library(prob)
library(gtools)
library(tidyverse)
library(here)
```

```{r}
titanic <- read_csv(here("data/titanic.csv"))
```

# Distinct values withing class

```{r}
distinct(titanic, class)
```

```{r}
titanic
```

```{r}
titanic_passengers <- titanic %>% 
  filter(class %in% c("1st", "2nd", "3rd"))
titanic_passengers
```

From the titanic data set we have 2,207 rows. When only people in the 1st, 2nd and 3rd class is search for, we are left with 1317 rows. 

Therefore, there is 1317 passengers. With that logic we can take away 1,317 from the 2,207 rows we originally started with to determine the number of crew.

2,207 - 1,317 = 890 

With the code bellow we can see this is correct.

```{r}
titanic_crew <- titanic %>% 
  filter(class %in% c("engineering crew",
                      "victualling crew",
                      "restaurant staff",
                      "deck crew",
                      "titanic_crew"))
titanic_crew
```

```{r}
titanic_passengers <- titanic_passengers %>% 
  filter(survived == "yes")
titanic_passengers
```

From the 1,317 passengers, only 500 survived

```{r}
titanic_crew <- titanic_crew %>% 
  filter(survived == "yes") 
titanic_crew
```

From the 890 crew, only 211 survived


You’re going to calculate the conditional probabilities prob( survived ∣ crew ) and prob( survived ∣ passenger ) to settle this dispute.

ANSWER

THERE IS:
  1,317 PASSENGERS
  890 CREW
  2,207 TOTAL
  
SURVIVED:
  500 PASSENGERS
  211 CREW
  711 TOTAL

prob of PASSENGERS = 500 / 1317 = 0.379 = 38%

prob of CREW = 211 / 890 = 0.237 = 24%




MVP and Extension - Probability problems

1. If I roll a six-sided dice once, what is the probability of getting a number less than 5?

ANSWER = 4/6 = 2/3

2. How many outcomes are there in the sample space of an experiment in which we toss three dice?

ANSWER 6^3 = 216


3. In an experiment where we roll four dice:

  1. how many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice         equals 5, 6 or 7)?

  ANSWER = 

  2. what is the probability of this event?
  
  ANSWER = 0.0261

  3. what assumptions do we apply in answering part ii?
  
  ANSWER = None of the dice can be 5 or higher and there can at minimum be 3 ones rolled.


6. If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?

ANSWER

52/2 = 26/2 = 12
Therefore the probability is 1/12 or 0.0833





