---
title: "R Notebook"
output: html_notebook
---

Wed 18th November 2020 - Homework - ggplot2 advanced

Calum Sey - CodeClan

1 Learning Objectives
Practice making plots with ggplot2
Create your own theme and use it with plots

2 Background
QikBit is a start-up company producing low cost fitness trackers. Their flagship product, the KwikBit Unit1 (spot the mistake on the patent form) reproduces the functionality of the best in class commercial fitness trackers, but is cheap to make. They are currently preparing to pitch to a potential investor and require a selection of charts to include in their presentation and promotional materials.

```{r}
library(tidyverse)
library(janitor)
library(CodeClanData)
```

3 Data
The data for this assignment is provided in the CodeClanData package.

qb_revenue_breakdown
qb_monthly_sales
qb_competitors
qb_device_data


```{r}
revenue_breakdown <- qb_revenue_breakdown
monthly_sales <- qb_monthly_sales
competitors <- qb_competitors
device_data <- qb_device_data
```

4.1 Part 1
1. Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

2. Make a line chart showing monthly sales of the “flagship product” - the KwikBit Unit1 - over the last year. This data is inside qb_monthly_sales, but you will need to use subset.

3. Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

4. Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.

5. Now show the sales from the 5 competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

6. Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between individuals and people. Data is in qb_device_data.


QUESTION
1. Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
revenue_breakdown
```

```{r}
ggplot(revenue_breakdown) +
  aes(x = Year,
      y = Revenue,
      fill = Product) +
  geom_col() 
```


QUESTION
2. Make a line chart showing monthly sales of the “flagship product” - the KwikBit Unit1 - over the last year. This data is inside qb_monthly_sales, but you will need to use subset.

```{r}
monthly_sales
```

```{r}
kwikbit <- subset(monthly_sales, Cashflow == "Kwikbit Unit 1 Sales")

ggplot(kwikbit) +
  aes(x = Date,
      y = Amount) +
  geom_line() 
```


QUESTION 3
3. Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}
revenue_2019 <- subset(monthly_sales, Cashflow != "Kwikbit Unit 1 Sales")

ggplot(revenue_2019) +
  aes(x = Date,
      y = Amount,
      colour = Cashflow) +
  geom_line() 
```


QUESTION 4
4. Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.

```{r}
competitors
```

```{r}
ggplot(competitors) +
  aes(x = Year,
      y = Revenue,
      fill = Company) +
  geom_area() 
```

QUESTION
5. Now show the sales from the 5 competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

```{r}
ggplot(competitors) +
  aes(x = Year,
      y = Revenue,
      colour = Company) +
  geom_line() +
  geom_point()
```

QUESTION
6. Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between individuals and people. Data is in qb_device_data.

```{r}
device_data
```

```{r}
ggplot(device_data) +
  aes(x = hours,
      y = counts) +
  geom_line() +
  facet_grid(id ~ device)
```

QUESTION
Part 2
Take the plots that you produced in part one and now polish them by:

1. Adding appropriate labels
2. Changing the scales and coordinates when appropriate.
3. Applying a unified theme, which is described below:

-Graphs should have white backgrounds, and use colour sparingly.
-There should be faint grid lines.
-Font sizes should be ~12pt although titles should be slightly larger and axis labels can   be slightly smaller.
-All plots should use colours from the following company colour scheme.

```{r}
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")
```

```{r}
theme_c <- theme(
  panel.background = element_rect(fill = "white"),
  panel.grid = element_line(colour = "grey"),
  plot.title = element_text(size = 16),
  axis.text = element_text(size = 10)
)
```

QUESTION
1. Adding appropriate labels

```{r}
ggplot(revenue_breakdown) +
  aes(x = Year,
      y = Revenue,
      fill = Product) +
  geom_col() +
  theme_qb +
  scale_fill_manual(values = col_scheme) +
  ggtitle("Revenue Breakdown")
```


```{r}
ggplot(kwikbit) +
  aes(x = Date,
      y = Amount) +
  geom_line() +
  theme_qb +
  ggtitle("Sales")
```









